---
title: "Coursera - Regression Models"
author: "Ha Kieu My"
date: "1 January 2016"
output: html_document
---

In this report, the data set "mtcars" data is analyzed to determine the relationship between the transmission type and fuel efficiency (miles per gallon) of automobiles. In particlular, these 2 questions are of interest:

  1) Is an automatic or manual transmission better for MPG?
  2) What is the MPG difference between automatic and manual transmissions?

The data set "mtcars" was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles.

Description of variables:
  mpg: Miles per gallon
  cyl: Number of cylinders
  disp: Displacement (cu.in.)
  hp: Gross horsepower
  drat: Rear axle ratio
  wt: Weight (lb/1000)
  qsec: Time to drive ¼ mile
  vs: V or ordinary engine
  am: Transmission (0 = automatic, 1 = manual)
  gear: Number of forward gears
  carb: Number of carburetors

The qualitative variables such as number of cylinders and gears were converted to factors.

```{r}
data(mtcars)
library(knitr)
mtcars$cyl <- factor(mtcars$cyl)
mtcars$vs <- factor(mtcars$vs)
mtcars$am <- factor(mtcars$am, labels = c("Automatic", "Manual"))
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
```

A Two Sample t-test is conducted between the different transmission types. The null hypothesis is that transmission types don't have an effect on MPG.

```{r}
t_test <- t.test(mpg ~ am, data = mtcars)
t_test
```

The null hypothesis is discarded for a p-value greater than 0.05. The p-value of 0.001374 and difference in means show that manual transmission has significantly more MPG than automatic.
Manual transmission has about 6 MPG more than automatics.

```{r}
boxplot(mpg ~ am, data = mtcars,
        xlab = "Transmission type", ylab = "Miles per gallon",
        main = "MPG vs Transmission", col = c("salmon", "steelblue"), 
        names = c("Automatic", "Manual"))
```

